Comparing vector-based and ACT-R memory models using large-scale datasets:\protect\\User-customized hashtag and tag prediction on Twitter and StackOverflow

### 2014-09-22 writeups/dissertation/dissertation.tex
foo

@@

@@

\subsubsection{Acknowledgements}

The majority of the modeling and analysis was done with the R statistical computing environment \parencite{RCoreTeam2014} and two important R packages:
data.table \parencite{Dowle2014} was leveraged to implement the models efficiently, and ggplot2 \parencite{Wickham2009} was used to produce the visualizations.

\subsubsection{Software Repository}

>>>>

% http://tex.stackexchange.com/questions/55780/disable-month-in-biblatex-bibliography
\AtEveryBibitem{\clearfield{month}}
\AtEveryCitekey{\clearfield{month}}

@@

\section{Acknowledgements}

I would first like to thank my advisor, Mike Byrne, for all of his feedback and suggestions for this dissertation research
and also his excellent guidance throughout my time as a graduate student.
I would also like to thank my parents, Mike and Patsy, for the positive influence that they have provided me for my entire life.
Finally, I would like to thank my brothers Brendan and Justin, sister Kellen, extended family, and friends, for all of their support during my time in the Rice Psychology graduate program.

This work was supported in part by the Gertrude Maurin Fund.
The resources were used to purchase high-performance computing hardware and the research would not have been possible without this crucial equipment.

I would also like to mention a few open-sourced software packages that were heavily leveraged to do this research:
The majority of the modeling and analysis was done with the R statistical computing environment \parencite{RCoreTeam2014} and two important R packages:
data.table \parencite{Dowle2014} was leveraged to implement the models efficiently, and ggplot2 \parencite{Wickham2009} was used to produce the visualizations.

\newpage

@@

\clearpage
\section{Appendix 1: Support Code}
